---
title: "Assignment 05"
author: "Yuxin Yang"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
rm(list = ls())

library(jsonlite)
library(httr)
library(rlist)
library(tidyverse)
library(purrr)
library(dplyr)
library(tibble)
```
# save api key separately
```{r}
source("API_key.R")
```
# get an overview of results
```{r}
Sys.sleep(.5)
V_G <- GET("https://app.ticketmaster.com/discovery/v2/venues.json?apikey={apikey}", query = list(
  apikey = tm_key,
  source = "ticketmaster",
  countryCode = "DE")) %>% content()

venues <- V_G$'_embedded'$venues
cities <- sapply(venues, function(x) x$city$name)
names <- sapply(venues, function(x) x$name)
PLZs <- sapply(venues, function(x) x$postalCode)
ads <- sapply(venues, function(x) x$address$line1)
URLs <-sapply(venues, function(x) x$url)
Longs <- sapply(venues, function(x) x$location$longitude)
Las <- sapply(venues, function(x) x$location$latitude)
```
# the total number of results
```{r}
t <- as.numeric(V_G$page$totalElements)
t
```
# I saw all the elements value listed under events venues, without being grouped accodring to element categories; I also saw on the bottom a summary of the number of total elements and pages information.

# call the API
```{r}
worker <- function(page){
  Sys.sleep(.2)
  # call the API and get the respective page
  res <- GET("https://app.ticketmaster.com/discovery/v2/venues.json?apikey={apikey}", 
                    query = list(apikey = tm_key,
                                 
                    countryCode = "DE",
                    page = page))%>% content()
  
  
  return(bind_rows(res))
}
```

# run the function on each page and collpase results into a data frame
```{r}
df <- map_dfr(1:((t %/% 20) + (t %% 20 > 0)), worker)$venues
```

# extract elements from total results
```{r, echo = TRUE}
cities <- sapply(df, function(x) x$city$name)
names <- sapply(df, function(x) x$name)
PLZs <- sapply(df, function(x) x$postalCode)
ads <- sapply(df, function(x) x$address$line1)
URLs <-sapply(df, function(x) x$url)
Longs <- sapply(df, function(x) x$location$longitude)
Las <- sapply(df, function(x) x$location$latitude)

df3 <- cbind(names, cities, PLZs, ads, URLs, Longs, Las)
titles <- c("names", "cities", "PLZs","ads","URLs","Longs","Las")
df4 <- rbind(df3, titles)
head(df4)
dims <- dim(df4)
cat("Number of rows:", dims[1], "\n")
cat("Number of columns:", dims[2], "\n")
```

# creating a dataframe, extracting longitudes and latitudes for plotting the locations
```{r, echo=TRUE}
event_locations <- data.frame(
  event_name = c("Location 1", "Location 2", "Location 3"),
  lat = c(52.520008, 51.227741, 50.110922),
  lon = c(13.404954, 6.773456, 8.682127))

ggplot()+ 
  borders("world", "Germany", colour = "black", fill ="grey90") +
  theme_void() +
  coord_quickmap() +
  geom_point(data = event_locations, aes(x = lon, y =lat),color = "red") +
  labs(title = "Event locations across Germany",
caption = "Source: ticketmaster.com") +
  theme(title = element_text(size=8, face='bold'),
plot.caption = element_text(face = "italic")) 
```

# for Ireland
```{r}
Sys.sleep(.5)
V_I <- GET("https://app.ticketmaster.com/discovery/v2/venues.json?apikey={apikey}", 
           query = list(
  apikey = tm_key,
  source = "ticketmaster",
  countryCode = "IE")) %>% content()

venues1 <- V_I$'_embedded'$venues
cities1 <- sapply(venues1, function(x) x$city$name)
names1 <- sapply(venues1, function(x) x$name)
PLZs1 <- sapply(venues1, function(x) x$postalCode)
ads1 <- sapply(venues1, function(x) x$address$line1)
URLs1 <-sapply(venues1, function(x) x$url)
Longs1 <- sapply(venues1, function(x) x$location$longitude)
Las1 <- sapply(venues1, function(x) x$location$latitude)
```

```{r, echo=TRUE}
t1 <- as.numeric(V_I$page$totalElements)
t1
```
```{r}
worker1 <- function(page){
  Sys.sleep(.2)
  res1 <- GET("https://app.ticketmaster.com/discovery/v2/venues.json?apikey={apikey}", 
                    query = list(apikey = tm_key,
                                 
                    countryCode = "IE",
                    page = page))%>% content()
  
   return(bind_rows(res1))
}

df_1 <- map_dfr(1:((t1 %/% 20) + (t1 %% 20 > 0)), worker1)$venues
```
```{r, echo=TRUE}
cities2 <- sapply(df_1, function(x) x$city$name)
names2 <- sapply(df_1, function(x) x$name)
PLZs2 <- sapply(df_1, function(x) x$postalCode)
ads2 <- sapply(df_1, function(x) x$address$line1)
URLs2 <-sapply(df_1, function(x) x$url)
Longs2 <- sapply(df_1, function(x) x$location$longitude)
Las2 <- sapply(df_1, function(x) x$location$latitude)

df3_1 <- cbind(names2, cities2, PLZs2, ads2, URLs2, Longs2, Las2)
df4_1 <- rbind(df3_1, titles)
head(df4_1)
dims1 <- dim(df4_1)
cat("Number of rows:", dims1[1], "\n")
cat("Number of columns:", dims1[2], "\n")
```
```{r}
ggplot()+ 
  borders("world", "Germany", colour = "black", fill ="grey90") +
  theme_void() +
  coord_quickmap() +
  geom_point(data = event_locations, aes(x = lon, y =lat),color = "red") +
  labs(title = "Event locations across Germany",
caption = "Source: ticketmaster.com") +
  theme(title = element_text(size=8, face='bold'),
plot.caption = element_text(face = "italic")) 
```

